### 2025-06-05 correlation.qmd
20250605 - typos

Also note that, although the the ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength of the (linear) association between two variables, it does not reflect the slope of that association, as depicted in @fig-correlationExamples.

::: {#fig-correlationExamples}
![](images/correlationExamples.png){fig-alt="Several sets of ($x$, $y$) points, with the the ([Pearson](#sec-correlationExamplesPearson)) correlation coefficient of $x$ and $y$ for each set. The the ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength and direction of a linear association (top row), but not the slope of that association (middle), nor many aspects of nonlinear associations (bottom). N.B.: the figure in the center has a slope of 0 but in that case the correlation coefficient is undefined because the variance of $y$ is zero. From <https://en.wikipedia.org/wiki/File:Correlation_examples2.svg>."}

Several sets of ($x$, $y$) points, with the the ([Pearson](#sec-correlationExamplesPearson)) correlation coefficient of $x$ and $y$ for each set. The the ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength and direction of a linear association (top row), but not the slope of that association (middle), nor many aspects of nonlinear associations (bottom). N.B.: the figure in the center has a slope of 0 but in that case the correlation coefficient is undefined because the variance of $y$ is zero. From <https://en.wikipedia.org/wiki/File:Correlation_examples2.svg>.
:::

>>>>

Also note that, although the ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength of the (linear) association between two variables, it does not reflect the slope of that association, as depicted in @fig-correlationExamples.

::: {#fig-correlationExamples}
![](images/correlationExamples.png){fig-alt="Several sets of ($x$, $y$) points, with the ([Pearson](#sec-correlationExamplesPearson)) correlation coefficient of $x$ and $y$ for each set. The ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength and direction of a linear association (top row), but not the slope of that association (middle), nor many aspects of nonlinear associations (bottom). N.B.: the figure in the center has a slope of 0 but in that case the correlation coefficient is undefined because the variance of $y$ is zero. From <https://en.wikipedia.org/wiki/File:Correlation_examples2.svg>."}

Several sets of ($x$, $y$) points, with the ([Pearson](#sec-correlationExamplesPearson)) correlation coefficient of $x$ and $y$ for each set. The ([Pearson](#sec-correlationExamplesPearson)) correlation reflects the strength and direction of a linear association (top row), but not the slope of that association (middle), nor many aspects of nonlinear associations (bottom). N.B.: the figure in the center has a slope of 0 but in that case the correlation coefficient is undefined because the variance of $y$ is zero. From <https://en.wikipedia.org/wiki/File:Correlation_examples2.svg>.
:::
